Self-Supervised Transfer Learning From 2D Images to 3D Point Clouds

### 2022-04-18 doc/paper.tex
adds CSC semantic seg results

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c c c c | c }
                                        & ceiling        & floor          & wall           & beam           & column         & window         & door           & table          & chair          & sofa           & bookcase       & board          & clutter        & mIOU                   \\
            \hline
            Scratch                     & 90.34          & \textbf{96.84} & 80.63          & 0              & 25.5           & 56.95          & 62.93          & 75.14          & 86.21          & 65.77          & 72.12          & 76.91          & 56.4           & 65.06                  \\
            Supervised                  & \textbf{91.81} & 96.74          & \textbf{84.11} & \textbf{0.21}  & \textbf{34.68} & \textbf{57.64} & \textbf{81.53} & \textbf{77.63} & \textbf{89.82} & \textbf{85.76} & \textbf{76.03} & \textbf{79.27} & \textbf{57.67} & \textbf{70.22} (+5.16) \\
            \hline
            PointContrast               & 91.97          & 96.67          & 82.4           & 0              & 17.84          & 56.49          & 75.39          & \textbf{77.63} & 87.35          & 63.3           & 73.53          & 79.55          & 58.76          & 66.22 (+1.16)          \\
            PointContrast - No Overhang & 91.624         & 96.86          & 82.02          & 0              & 29.37          & \textbf{57.5}  & 64.93          & 75.49          & 87.36          & 59.32          & 71.42          & 76.61          & 56.11          & 65.28 (+0.22)          \\
            CME \textbf{(Ours)}         & 90.8           & 96.57          & \textbf{82.52} & \textbf{0.110} & \textbf{30.94} & 56.94          & 68.71          & 75.12          & \textbf{88.48} & \textbf{71.7}  & \textbf{72.17} & 73.783         & \textbf{56.35} & 66.48 (+1.42)          \\
        \end{tabular}
    }
    \caption{S3DIS Semantic Segmentation results (mIOU)}
    \label{table:s3disResults}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.8\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c | c }
                                & beam & column        & window        & door & table         & chair         & sofa          & bookcase      & board         & clutter       & mAP@0.5              \\
            \hline
            Scratch             & 0    & 12.8          & 61.7          & 92.0 & 51.4          & 87.3          & 62.4          & 38.5          & 87.0          & 37.1          & 53.0                 \\
            Supervised          & 0    & 26.0          & 74.3          & 84.5 & 43.3          & 87.3          & \textbf{81.8} & 37.4          & \textbf{85.4} & \textbf{41.2} & \textbf{56.2} (+3.2) \\
            \hline
            PointContrast       &      & 24.7          & 67.9          & 90.7 & 43.8          & 92.0          & 72.7          & 32.3          & 85.6          & 38.0          & 54.8 (+1.8)          \\
            CME \textbf{(Ours)} & 0    & \textbf{35.0} & \textbf{70.0} & 83.4 & \textbf{53.9} & \textbf{88.9} & 71.7          & \textbf{42.2} & 76.1          & 36.7          & 55.8 (+2.8)          \\
        \end{tabular}
    }
    \caption{S3DIS Instance Segmentation Results (mAP@0.5)}
    \label{table:s3disInstanceSegmention}
\end{table*}

\begin{table}[t!]
    \centering

    \begin{tabular}{ c | c c c c c c}
                            & 5\%  & 10\% & 20\% & 30\% & 40\% & 100\% \\
        \hline
        Scratch             & 56.9 &      & 64.1 &      & 65.6 &       \\
        \hline
        PointContrast       &      &      &      &      &      &       \\
        CME \textbf{(Ours)} & 60.8 &      & 64.8 &      & 64.7 &       \\
    \end{tabular}

    \caption{Scannet Semantic Segmentation with Partial Data  (mIOU)}
    \label{table:scannetVaryingDataAmount}
\end{table}

@@

%     \begin{tabular}{ c | c c c c c c }
%                             & 5\% & 10\% & 20\% & 30\% & 40\% & 100\% \\
%         \hline
%         Scratch             &     &      &      &      &      &       \\
%         \hline
%         PointContrast       &     &      &      &      &      &       \\
%         CME \textbf{(Ours)} &     &      &      &      &      &       \\
%     \end{tabular}

%     \caption{S3DIS Semantic Segmentation with Partial Data  (mIOU)}
%     \label{table:s3disVaryingDataAmount}
% \end{table}

@@

Things to include in results
\begin{itemize}
    \item S3DIS semantic segmentation
    \item S3DIS instance segmentation
    \item Scannet semantic segmentation
    \item Scannet semantic segmentation with different amounts of data
    \item Visualization of features in 2D
    \item Visualization of features in 3D
    \item Pretraining and training without colour information
    \item Using projection of 3D points instead of direct scan using \cite{katz2007Direct}
    \item Training and validation curves
    \item Ablation studies
\end{itemize}

>>>>

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c c c c | c }
                                       & ceiling        & floor          & wall           & beam           & column         & window         & door           & table          & chair          & sofa           & bookcase       & board          & clutter        & mIOU                   \\
            \hline
            Scratch                    & 90.34          & \textbf{96.84} & 80.63          & 0              & 25.5           & 56.95          & 62.93          & 75.14          & 86.21          & 65.77          & 72.12          & 76.91          & 56.4           & 65.06                  \\
            Supervised                 & \textbf{91.81} & 96.74          & \textbf{84.11} & \textbf{0.21}  & \textbf{34.68} & \textbf{57.64} & \textbf{81.53} & \textbf{77.63} & \textbf{89.82} & \textbf{85.76} & \textbf{76.03} & \textbf{79.27} & \textbf{57.67} & \textbf{70.22} (+5.16) \\
            \hline
            PointContrast              & 91.97          & \textbf{96.67} & 82.4           & 0              & 17.84          & 56.49          & \textbf{75.39} & \textbf{77.63} & 87.35          & 63.3           & 73.53          & \textbf{79.55} & 58.76          & 66.22 (+1.16)          \\
            PointContrast - Same Scan  & 91.03          & 96.27          & \textbf{82.8}  & 0              & 31.53          & 57.27          & 69.33          & 76.97          & \textbf{88.83} & 45.49          & 71.02          & 77.09          & 57.06          & 64.97 (-0.09)          \\
            Contrastive Scene Contexts & \textbf{92.34} & 96.02          & 83.53          & 0              & \textbf{40.88} & \textbf{57.73} & 72.11          & 77.5           & 88.15          & \textbf{74.61} & \textbf{74.52} & 76.45          & \textbf{62.64} & \textbf{68.96} (+3.9)  \\
            CME \textbf{(Ours)}        & 90.8           & 96.57          & 82.52          & \textbf{0.110} & 30.94          & 56.94          & 68.71          & 75.12          & 88.48          & 71.7           & 72.17          & 73.783         & 56.35          & 66.48 (+1.42)          \\
        \end{tabular}
    }
    \caption{S3DIS Semantic Segmentation results (mIOU)}
    \label{table:s3disResults}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.8\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c c c c c | c }
                                & beam & column        & window        & door & table         & chair         & sofa          & bookcase      & board         & clutter       & mAP@0.5              \\
            \hline
            Scratch             & 0    & 12.8          & 61.7          & 92.0 & 51.4          & 87.3          & 62.4          & 38.5          & 87.0          & 37.1          & 53.0                 \\
            Supervised          & 0    & 26.0          & 74.3          & 84.5 & 43.3          & 87.3          & \textbf{81.8} & 37.4          & \textbf{85.4} & \textbf{41.2} & \textbf{56.2} (+3.2) \\
            \hline
            PointContrast       & 0    & 24.7          & 67.9          & 90.7 & 43.8          & 92.0          & 72.7          & 32.3          & 85.6          & 38.0          & 54.8 (+1.8)          \\
            CME \textbf{(Ours)} & 0    & \textbf{35.0} & \textbf{70.0} & 83.4 & \textbf{53.9} & \textbf{88.9} & 71.7          & \textbf{42.2} & 76.1          & 36.7          & 55.8 (+2.8)          \\
        \end{tabular}
    }
    \caption{S3DIS Instance Segmentation Results (mAP@0.5)}
    \label{table:s3disInstanceSegmention}
\end{table*}

@@

%     \begin{tabular}{ c | c c c c c c}
%                             & 5\%  & 10\% & 20\% & 30\% & 40\% & 100\% \\
%         \hline
%         Scratch             & 56.9 &      & 64.1 &      & 65.6 &       \\
%         \hline
%         PointContrast       &      &      &      &      &      &       \\
%         CME \textbf{(Ours)} & 60.8 &      & 64.8 &      & 64.7 &       \\
%     \end{tabular}

%     \caption{Scannet Semantic Segmentation with Partial Data  (mIOU)}
%     \label{table:scannetVaryingDataAmount}
% \end{table}

\begin{table}[t!]
    \centering
    \resizebox{0.4\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                & 5\%   & 10\%  & 20\%  & 30\%  & 40\%  & 100\% \\
            \hline
            Scratch             & 42.2  & 51.09 & 58.23 & 59.23 & 62.17 & 67.43 \\
            \hline
            PointContrast       & 44.79 & 55.28 & 57.98 & 58.97 & 63.17 &       \\
            CME \textbf{(Ours)} & 44.04 & 51.19 & 57.3  & 60.73 & 63.31 & 67.71 \\
        \end{tabular}
    }
    \caption{Scannet Semantic Segmentation with Partial Data  (mIOU)}
    \label{table:scannetVaryingDataAmount}
\end{table}

@@

\textbf{IDEA:} To test the overlap hypothesis, try upping the min overlap ratio from 0.3 to 0.9.

Things to include in results
\begin{itemize}
    \item S3DIS semantic segmentation
    \item S3DIS instance segmentation
    \item Scannet semantic segmentation
    \item Scannet semantic segmentation with different amounts of data
    \item Visualization of features in 2D
    \item Visualization of features in 3D
          % \item Pretraining and training without colour information
    \item Using projection of 3D points instead of direct scan using \cite{katz2007Direct}
    \item Training and validation curves
    \item Ablation studies
\end{itemize}
